Making Sequential Programs Deterministic

### 2019-04-03 related.tex
flake related

\todo{A NonDet annotation:
  \url{http://www.swi-prolog.org/pldoc/man?section=modes}}

>>>>

DeFlaker~\cite{deflaker} is another approach for flake test detection. It relies on
version control history to detect tests that behave differently. It computes a diff of the code covered
in the current version and the previous one. If there exists a tests case whose code coverage does not include
this diff but still produces different results on the two versions being compared, it is flagged as being flaky.
This approach doesn't require JVM modifications
and integrates easily with a production software. DeFlaker reported 19 previously unknown bugs
in open source projects, 7 of which were addressed by the developers of these projects.

~\cite{LuoHEM2014} study 51 open source projects and analyze the most common root causes of
test flakiness. The findings in the paper suggest that most of the flakiness in tests is caused by
the use of async away, concurrency, or due to test order dependency.~\cite{Plotkin:1993:LPP:645891.671433}
performs an empirical study on open source benchmarks that concur with the results of~\cite{LuoHEM2014}.
Additionally, the authors of this paper study the effects of removing these test smells. Their results suggest that
refactoring the test code smells fixed more than half of the identified flaky tests.
\todo{A NonDet annotation:
  \url{http://www.swi-prolog.org/pldoc/man?section=modes}}
